---
title: "Inter-rater reliability — Ketamine clinics"
format: 
  html:
    toc: true
    code-fold: true
    code-summary: "Show Code"
    self-contained: true
---

## Project Code Settings

```{r setup}

#| include: false
#| message: false
#| warning: false

knitr::opts_chunk$set(
  eval = T, warning = F, message = F, echo = T, fig.dim = c(6,3), fig.width = 9, fig.height = 5, dpi = 300, fig.pos = "!h"
)

packages = c("tidyverse","arsenal","kableExtra")



suppressWarnings(
  suppressPackageStartupMessages(invisible(lapply(packages, require, character.only = T))))


theme_set(theme_minimal()+
            theme(legend.position = "bottom")+
            theme(plot.title = element_text(hjust = 0.5, size = 12),
                  plot.subtitle= element_text(hjust = 0.5, size = 8)))

custom_cat_test <- function(currcol, bycol, 
                            chisq.correct = FALSE, 
                            simulate.p.value = FALSE, 
                            B = 2000, 
                            wilcox.correct, 
                            wilcox.exact, 
                            test.always, 
                            ...) {
  # Create the contingency table
  tab <- table(currcol, bycol)
  
  # Attempt chi-square test without continuity correction (as specified)
  chisq_result <- try(chisq.test(tab, 
                                 correct = chisq.correct, 
                                 simulate.p.value = simulate.p.value, 
                                 B = B),
                      silent = TRUE)
  
  # If the test fails or expected counts are below 5, use Fisher's exact test
  if (inherits(chisq_result, "try-error") || any(chisq_result$expected < 5)) {
    fisher_result <- fisher.test(tab, ...)
    p_val <- fisher_result$p.value
    method_used <- "Fisher's Exact Test"
  } else {
    p_val <- chisq_result$p.value
    method_used <- "Chi-Squared Test"
  }
  
  # Return a list with at least the p-value
  return(list(p.value = p_val, method = method_used))
}

my_controls <- arsenal::tableby.control(
  test = T,
  total = T,
  numeric.test = "kwt", cat.test = "custom_cat_test",
  numeric.stats = c("N", "meansd", "medianq1q3", "range", "Nmiss2"),
  cat.stats = c("countpct", "Nmiss2"),
  stats.labels = list(
    meansd = "Mean (SD)",
    medianq1q3 = "median (Q1, Q3)",
    range = "Min - Max",
    Nmiss2 = "Missing"
  )
)
  
my_controls_row <- arsenal::tableby.control(
  test = T,
  total = T,
  numeric.test = "kwt", cat.test ="custom_cat_test",
  numeric.stats = c("N", "meansd", "medianq1q3", "range", "Nmiss2"),
  cat.stats = c("countrowpct", "Nmiss2"),
  stats.labels = list(
    meansd = "Mean (SD)",
    medianq1q3 = "median (Q1, Q3)",
    range = "Min - Max",
    Nmiss2 = "Missing"
  )
)

#quarto::quarto_render("First Pass.qmd")

```

## Overview

The goal of this analysis is to determine if there is reliability among responses by four raters to various instruments that answer `56` binary (yes/no) questions about `233` Ketamine clinics in the tristate area (NY, NJ, CT). In order to determine reliability we used a Fleiss' Kappa score that accounts for having more than two raters. Reliability scores greater than or equal to `0.60` suggest agreement between raters.

## Data Management

This section contains how the data set is wrangled for analysis. Here are a list of data considerations used to prepare the data for analysis.

-   removed disagreement columns, and timestamp
-   removed other disorders column because they are expand as individual columns
-   reshaped the data to conduct the IRR analysis including all 4 raters
-   attempts to concatenate location, an clinic types
-   removed clinics that had missing observations

```{r}

data = readxl::read_xlsx("./data/KETAMINE_updated.xlsx") %>% # reading in data
  janitor::clean_names() %>% # making all column names lowercase
  select(-contains("disagreement")) %>% # getting rid of pre calculated disagreement by collaborator
  
  #These are the names of clinics that were causing the error
  
 ## filter(clinic_name %in% c("Dr Vs Med Spa","Dr. V's Med Spa","Mar Y Sol Mental Health Experts","Mar y Sol Mental Health Experts",
##                                "Rise And Mind","Rise and Mind","Trifecta Health","Trifecta Health NYC", "Turn The Mind","Turn the Mind")) %>% 
  
  ## reordering data set column names, and removing variables that are not responses to questions by raters
  
  
  select(clinic_name, rater,contains("location"), contains("clinic"), everything(), -other_disorders, - timestamp) %>% 
  mutate(
    clinic_name = recode(clinic_name,"Dr Vs Med Spa"="Dr. V's Med Spa", 
                         "Mar Y Sol Mental Health Experts" ="Mar y Sol Mental Health Experts",
                        "Rise And Mind"="Rise and Mind",
                        "Trifecta Health" ="Trifecta Health NYC",
                         "Turn The Mind"="Turn the Mind")
  )

# 
# data3 = readxl::read_xlsx("./data/Ketamine clinic ratings 3-4-25.xlsx") %>% # reading in data
#   janitor::clean_names() %>% # making all column names lowercase
#   select(-contains("disagreement")) %>%
#    select(clinic_name, rater,contains("location"), contains("clinic"), everything(), -other_disorders) #%>%
#    filter(clinic_name %in% c("Dr Vs Med Spa","Dr. V's Med Spa","Mar Y Sol Mental Health Experts","Mar y Sol Mental Health Experts",
#                               "Rise And Mind","Rise and Mind","Trifecta Health","Trifecta Health NYC", "Turn The Mind","Turn the Mind")) %>%
#   arrange(clinic_name,rater)


data_d = readxl::read_xlsx("./data/KETAMINE_updated.xlsx") %>% # reading in data
  janitor::clean_names() %>% # making all column names lowercase
   select(clinic_name, rater,contains("location"), 
          contains("clinic"), everything(), 
          -other_disorders,
          - timestamp,
          -contains("disagreement")) %>% 
  mutate(
    clinic_name = recode(clinic_name,"Dr Vs Med Spa"="Dr. V's Med Spa", 
                         "Mar Y Sol Mental Health Experts" ="Mar y Sol Mental Health Experts",
                        "Rise And Mind"="Rise and Mind",
                        "Trifecta Health" ="Trifecta Health NYC",
                         "Turn The Mind"="Turn the Mind")
  ) %>% 
  
  
  # building majority rule dataset
  filter(!rater == 3) %>% 
  pivot_longer(
   location_ny:other_tbi,
   names_to = "questions",
   values_to = "responses"
 ) %>% 
    group_by(clinic_name, questions) %>% 
    mutate(
      majority = if_else(mean(responses)>=0.5,1L,0L)
    ) %>% 
    
    
    #filter(grepl("location",questions,ignore.case = T)) %>% 
   # arrange(clinic_name, questions,rater) %>% 
    select(-rater, -responses) %>% 
    unique()  %>% 
    
    pivot_wider(
      names_from = questions,
      values_from = majority
    ) %>%
    ungroup() %>% 
  # concatenating state variables
  mutate(state = case_when( 
    location_ny == 1 & !location_nj == 1 & !location_ct == 1 ~"New York",
    !location_ny == 1 & location_nj == 1 & !location_ct == 1 ~"New Jersey",
    !location_ny == 1 & !location_nj == 1 & location_ct == 1 ~"Connecticut",
    TRUE ~ "combination"
  )
#   ,
#   
#   # concatenating clinic types
#   clinic_type = case_when(
#   clinic_individual == 1 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 0 ~ "individual only",
#   clinic_individual == 0 & clinic_chain == 1 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 0 ~ "chain only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 1 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 0 ~ "hospital only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 0 & clinic_home == 0 ~ "med_spa only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "telehealth only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 1 ~ "home only",
#   
#   clinic_individual == 1 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "individual + tele",
#   
#   clinic_individual == 0 & clinic_chain == 1 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "chain only + tele",
#   
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 1 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "hospital only + tele",
#   
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 1 & clinic_home == 0 ~ "med_spa only + tele",
#   
#   
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 1 ~ "home only + tele",
#   
#     clinic_individual == 0 & clinic_chain == 1 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 0 & clinic_home == 0 ~ "chain + med-spa",
#   
#       clinic_individual == 1 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 0 & clinic_home == 0 ~ "individual + med-spa",
#   
#   TRUE ~ NA_character_
# )
  ) %>% 
  mutate_at(vars(location_ny:other_tbi),as.character)
 # filter(clinic_name %in% c("Dr Vs Med Spa","Dr. V's Med Spa","Mar Y Sol Mental Health Experts","Mar y Sol Mental Health Experts",
#                                "Rise And Mind","Rise and Mind","Trifecta Health","Trifecta Health NYC", "Turn The Mind","Turn the Mind")) %>% 
  
  #reordering data set column names, and removing variables that are not responses to questions by raters
  

data_3 = readxl::read_xlsx("./data/KETAMINE_updated.xlsx") %>% # reading in data
  janitor::clean_names() %>% # making all column names lowercase
   select(clinic_name, rater,contains("location"), 
          contains("clinic"), everything(), 
          -other_disorders,
          - timestamp,
          -contains("disagreement")) %>% 
  mutate(
    clinic_name = recode(clinic_name,"Dr Vs Med Spa"="Dr. V's Med Spa", 
                         "Mar Y Sol Mental Health Experts" ="Mar y Sol Mental Health Experts",
                        "Rise And Mind"="Rise and Mind",
                        "Trifecta Health" ="Trifecta Health NYC",
                         "Turn The Mind"="Turn the Mind")
  ) %>% 
  filter(rater == 3) %>% 
 
  # concatenating state variables
  mutate(state = case_when( 
    location_ny == 1 & !location_nj == 1 & !location_ct == 1 ~"New York",
    !location_ny == 1 & location_nj == 1 & !location_ct == 1 ~"New Jersey",
    !location_ny == 1 & !location_nj == 1 & location_ct == 1 ~"Connecticut",
    TRUE ~ "combination"
  )
#   ,
#   
#   # concatenating clinic types
#   clinic_type = case_when(
#   clinic_individual == 1 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 0 ~ "individual only",
#   clinic_individual == 0 & clinic_chain == 1 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 0 ~ "chain only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 1 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 0 ~ "hospital only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 0 & clinic_home == 0 ~ "med_spa only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "telehealth only",
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 0 & clinic_home == 1 ~ "home only",
#   
#   clinic_individual == 1 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "individual + tele",
#   
#   clinic_individual == 0 & clinic_chain == 1 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "chain only + tele",
#   
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 1 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 0 ~ "hospital only + tele",
#   
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 1 & clinic_home == 0 ~ "med_spa only + tele",
#   
#   
#   clinic_individual == 0 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 0 & clinic_telehealth == 1 & clinic_home == 1 ~ "home only + tele",
#   
#     clinic_individual == 0 & clinic_chain == 1 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 0 & clinic_home == 0 ~ "chain + med-spa",
#   
#       clinic_individual == 1 & clinic_chain == 0 & clinic_hospital == 0 &
#     clinic_med_spa == 1 & clinic_telehealth == 0 & clinic_home == 0 ~ "individual + med-spa",
#   
#   TRUE ~ NA_character_
# )
  ) %>% 
  mutate_at(vars(location_ny:other_tbi),as.character)
  
  
 data = readxl::read_xlsx("ketamine data all rater .xlsx")
```

## IRR Analysis

### IRR Analysis overall

::: panel-tabset


#### Pair-wise (2)

```{r}

combn(c("0","1","2","3"),2, simplify = F) %>% 
  map_dfr(~{
    pair_data = data %>% 
  
  
  # creating a response id for each rater (basically a response for every clinic)
  group_by(rater) %>% 
   mutate(response_id = row_number()) %>% 
  
  # reshaping the dataset to match form of the irr package 
  pivot_longer(cols = location_ny:other_tbi,
    names_to = "questions",
    values_to = "responses"
  ) %>% 
  pivot_wider(
    names_from = rater,
    values_from = responses
  ) %>% 
  
  # making the raters responses factors
  mutate_at(vars(`0`,`1`,`2`,`3`),factor) %>% 
  # only retaining the responses of each rater for the analysis (removing id columns)
  select(-response_id, -questions) %>% 
# conducting anlaysis for overall level of agreement
    select(all_of(.x))
    
    
# compute kappa
    kappa_val = irr::kappa2(pair_data)$value
    
# make table 
    tibble(rater1 = .x[1], rater2 = .x[2], kappa = kappa_val)
  }) %>% 
  
# arrange scores
  arrange(-kappa) %>% 
  
# formatt table 
  formattable::formattable()





```

#### Pair-wise (3)

```{r}



combn(c("0","1","2","3"),3, simplify = F) %>% 
  map_dfr(~{
    pair_data = data %>% 
  
  
  # creating a response id for each rater (basically a response for every clinic)
  group_by(rater) %>% 
   mutate(response_id = row_number()) %>% 
  
  # reshaping the dataset to match form of the irr package 
  pivot_longer(cols = location_ny:other_tbi,
    names_to = "questions",
    values_to = "responses"
  ) %>% 
  pivot_wider(
    names_from = rater,
    values_from = responses
  ) %>% 
  
  # making the raters responses factors
  mutate_at(vars(`0`,`1`,`2`,`3`),factor) %>% 
  # only retaining the responses of each rater for the analysis (removing id columns)
  select(-response_id, -questions) %>% 
# conducting anlaysis for overall level of agreement
    select(all_of(.x))
    
    
# compute kappa
    kappa_val = irr::kappam.fleiss(pair_data)$value
    
# make table 
    tibble(rater1 = .x[1], rater2 = .x[2], rater3 = .x[3], kappa = kappa_val)
  }) %>% 
  
# arrange scores
  arrange(-kappa) %>% 
  
# format table 
  formattable::formattable()




```

:::



### IRR Analysis group


::: panel-tabset

#### pair-wise (2)

In this section the Kappa scores for groups that include more than one instrument are presented.

```{r}


group_data = data %>% 
  
  
  # creating a response id for each rater (basically a response for every clinic)
  group_by(rater) %>% 
   mutate(response_id = row_number()) %>% 
  rename_at(vars(depression:eating_disorders),~paste0("disorder_",.)) %>% 
  
  # reshaping the dataset to match form need for the irr package 
  pivot_longer(cols = location_ny:other_tbi,
    names_to = "questions",
    values_to = "responses"
  ) %>% 
  pivot_wider(
    names_from = rater,
    values_from = responses
  ) %>% 
  mutate(question_group = case_when(
    grepl("location",questions,ignore.case = T)~ "location",
     grepl("visits",questions,ignore.case = T)~ "visits",
     grepl("types",questions,ignore.case = T)~ "types",
     grepl("form",questions,ignore.case = T)~ "form",
     grepl("clinic",questions,ignore.case = T)~ "clinic",
     grepl("degree",questions,ignore.case = T)~ "degree",
    grepl("cost",questions,ignore.case = T)~ "cost",
    grepl("insurance",questions,ignore.case = T)~ "insurance",
    grepl("disorder",questions,ignore.case = T)~ "conditions",
    grepl("promotional",questions,ignore.case = T)~ "promotional",
    grepl("benefits",questions,ignore.case = T)~ "benefits",
    grepl("citations",questions,ignore.case = T)~ "citations",
    grepl("risk",questions,ignore.case = T)~ "risk",
    grepl("other",questions,ignore.case = T)~ "other_conditions"
    
  )) %>% 
  
  # making the raters responses factors
  mutate_at(vars(`0`,`1`,`2`,`3`),factor) 


# creating table of kappa scores by group
  
   group_data %>% 
      filter(question_group %in% c("visits","clinic","location","form","conditions","other_conditions")) %>% 
      group_by(question_group) %>% 
      nest() %>% 
  mutate(pairwise = map(data, function(df){
                          combn(c("0","1","2","3"),2, simplify = F) %>% 
                            map_dfr(function(pair_cols){
                              tibble(
                                rater1 = pair_cols[1],
                                rater2 = pair_cols[2],
                                kappa = irr::kappa2(df %>%  select(all_of(pair_cols)))$value
                              )
                            })
                        })) %>% 
  unnest(pairwise) %>% 
     select(question_group, rater1, rater2, kappa) %>% 
    arrange(question_group,-kappa) %>%
    #rename("Group" = "groups", "Kappa Score"= "kapp_score") %>% 
    formattable::formattable()
  
```


#### pair-wise (3)

In this section the Kappa scores for groups that include more than one instrument are presented.

```{r}


# creating table of kappa scores by group
  
   group_data %>% 
      filter(question_group %in% c("visits","clinic","location","form","conditions","other_conditions")) %>% 
      group_by(question_group) %>% 
      nest() %>% 
  mutate(pairwise = map(data, function(df){
                          combn(c("0","1","2","3"),3, simplify = F) %>% 
                            map_dfr(function(pair_cols){
                              tibble(
                                rater1 = pair_cols[1],
                                rater2 = pair_cols[2],
                                rater3 = pair_cols[3],
                                kappa = irr::kappam.fleiss(df %>%  select(all_of(pair_cols)))$value
                              )
                            })
                        })) %>% 
  unnest(pairwise) %>% 
     select(question_group, rater1, rater2, rater3, kappa) %>% 
    arrange(question_group,-kappa) %>%
    #rename("Group" = "groups", "Kappa Score"= "kapp_score") %>% 
    formattable::formattable()
  
```


:::

### IRR Analysis Instrument


::: panel-tabset

#### pair-wise (2)

In this section the Kappa scores for individual instruments

```{r}


# creating table of kappa scores by instrument
  
   group_data %>% 
      group_by(questions) %>% 
      nest() %>% 
  mutate(pairwise = map(data, function(df){
                          combn(c("0","1","2","3"),2, simplify = F) %>% 
                            map_dfr(function(pair_cols){
                              tibble(
                                rater1 = pair_cols[1],
                                rater2 = pair_cols[2],
                                kappa = irr::kappa2(df %>%  select(all_of(pair_cols)))$value
                              )
                            })
                        })) %>% 
  unnest(pairwise) %>% 
     select(questions, rater1, rater2, kappa) %>% 
    arrange(questions,-kappa) %>%
    #rename("Group" = "groups", "Kappa Score"= "kapp_score") %>% 
    formattable::formattable()
  
```


#### pair-wise (3)

In this section the Kappa scores for individual instruments

```{r}


# creating table of kappa scores by instrument
  
   group_data %>% 
      group_by(questions) %>% 
      nest() %>% 
  mutate(pairwise = map(data, function(df){
                          combn(c("0","1","2","3"),3, simplify = F) %>% 
                            map_dfr(function(pair_cols){
                              tibble(
                                rater1 = pair_cols[1],
                                rater2 = pair_cols[2],
                                 rater3 = pair_cols[3],
                                kappa = irr::kappam.fleiss(df %>%  select(all_of(pair_cols)))$value
                              )
                            })
                        })) %>% 
  unnest(pairwise) %>% 
     select(questions, rater1, rater2, rater3, kappa) %>% 
    arrange(questions,-kappa) %>%
    #rename("Group" = "groups", "Kappa Score"= "kapp_score") %>% 
    formattable::formattable()
  
```


:::

### IRR Analysis by clinic

In this section the Kappa scores by clinic

::: panel-tabset

#### pair-wise (2)



```{r}

#preping data:

data2 = data %>% 
  group_by(rater) %>% 
  # mutate(response_id = row_number()) %>% 
  rename_at(vars(depression:eating_disorders),~paste0("disorder_",.)) %>% 
  
  # reshaping the dataset to match form need for the irr package 
  pivot_longer(cols = location_ny:other_tbi,
    names_to = "questions",
    values_to = "responses"
  ) %>% 
  pivot_wider(
    names_from = rater,
    values_from = responses
  ) %>% 
  mutate(question_group = case_when(
    grepl("location",questions,ignore.case = T)~ "location",
     grepl("visits",questions,ignore.case = T)~ "visits",
     grepl("types",questions,ignore.case = T)~ "types",
     grepl("form",questions,ignore.case = T)~ "form",
     grepl("clinic",questions,ignore.case = T)~ "clinic",
     grepl("degree",questions,ignore.case = T)~ "degree",
    grepl("cost",questions,ignore.case = T)~ "cost",
    grepl("insurance",questions,ignore.case = T)~ "insurance",
    grepl("disorder",questions,ignore.case = T)~ "conditions",
    grepl("promotional",questions,ignore.case = T)~ "promotional",
    grepl("benefits",questions,ignore.case = T)~ "benefits",
    grepl("citations",questions,ignore.case = T)~ "citations",
    grepl("risk",questions,ignore.case = T)~ "risk",
    grepl("other",questions,ignore.case = T)~ "other_conditions"
    
  )) %>% 
  
  # making the raters responses factors
  mutate_at(vars(`0`,`1`,`2`,`3`),factor) 


# creating table of kappa scores by instrument
  # Dr Vs Med Spa only has information from rater 0
   data2 %>% 
      group_by(clinic_name) %>% 
      nest() %>% 
  mutate(pairwise = map(data, function(df){
                          combn(c("0","1","2","3"),2, simplify = F) %>% 
                            map_dfr(function(pair_cols){
                              tibble(
                                rater1 = pair_cols[1],
                                rater2 = pair_cols[2],
                                kappa = irr::kappa2(df %>%  select(all_of(pair_cols)))$value
                              )
                            })
                        })) %>% 
  unnest(pairwise) %>% 
     select(clinic_name, rater1, rater2, kappa) %>% 
    arrange(clinic_name,-kappa) %>%
    rename("Clinic" = "clinic_name") %>% 
    formattable::formattable()
  
```






#### pair-wise (3)

In this section the Kappa scores for individual instruments

```{r}


# creating table of kappa scores by instrument
  
     data2 %>% 
      group_by(clinic_name) %>% 
      nest() %>% 
  mutate(pairwise = map(data, function(df){
                          combn(c("0","1","2","3"),3, simplify = F) %>% 
                            map_dfr(function(pair_cols){
                              tibble(
                                rater1 = pair_cols[1],
                                rater2 = pair_cols[2],
                                rater3 = pair_cols[3],
                                kappa = irr::kappam.fleiss(df %>%  select(all_of(pair_cols)))$value
                              )
                            })
                        })) %>% 
  unnest(pairwise) %>% 
     select(clinic_name, rater1, rater2, rater3, kappa) %>% 
    arrange(clinic_name,-kappa) %>%
    rename("Clinic" = "clinic_name") %>% 
    formattable::formattable()
  
```

:::



## Descriptive Statistics



### State + combination

::: panel-tabset

#### Among raters 1,2,3

We used majority rules to assign binary indicator for individual instruments. Given there are 3 independent raters there are no ties. 



```{r, results='asis'}

 arsenal::tableby(state ~ ., data = data_d %>% select(-clinic_name, -contains("location"),location_virtual), control = my_controls) %>% 
  summary()

```

#### Among rater 4

These are descriptive tables using only rater 4's responses. 

```{r, results='asis'}


arsenal::tableby(state ~ ., data = data_3 %>% select(-clinic_name,-rater, -contains("location"),location_virtual), control = my_controls) %>% 
  summary()

```

:::

### State + no combination

::: panel-tabset

#### Among raters 1,2,3

We used majority rules to assign binary indicator for individual instruments. Given there are 3 independent raters there are no ties. 


```{r, results='asis'}


arsenal::tableby(state ~ ., data = data_d %>% select(-clinic_name, -contains("location"),location_virtual) %>% filter(!state == "combination" ), control = my_controls) %>% 
  summary()

```


#### Among rater 4

These are descriptive tables using only rater 4's responses. 

```{r, results='asis'}


arsenal::tableby(state ~ ., data = data_3 %>% select(-clinic_name,-rater, -contains("location"),location_virtual) %>% filter(!state == "combination" ), control = my_controls) %>% 
  summary()

```

:::

### Virtual Location

::: panel-tabset

#### Among raters 1,2,3

We used majority rules to assign binary indicator for individual instruments. Given there are 3 independent raters there are no ties. 


```{r, results='asis'}

arsenal::tableby(location_virtual ~ ., data = data_d %>% select(-clinic_name,  -contains("location"),location_virtual), control = my_controls) %>% 
  summary()
```

#### Among rater 4

These are descriptive tables using only rater 4's responses. 


```{r, results='asis'}

arsenal::tableby(location_virtual ~ ., data = data_3 %>% select(-clinic_name,-rater,  -contains("location"),location_virtual), control = my_controls) %>% 
  summary()
```

:::


### Virtual Visits

::: panel-tabset

#### Among raters 1,2,3

We used majority rules to assign binary indicator for individual instruments. Given there are 3 independent raters there are no ties. 

```{r, results='asis'}
arsenal::tableby(visits_virtual ~ ., data = data_d %>% select(-clinic_name, -contains("location"),location_virtual), control = my_controls) %>% 
  summary()
```


#### Among rater 4

These are descriptive tables using only rater 4's responses. 


```{r, results='asis'}
arsenal::tableby(visits_virtual ~ ., data = data_3 %>% select(-clinic_name,-rater, -contains("location"),location_virtual), control = my_controls) %>% 
  summary()
```

:::
